Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-04-03 WSSSPE1_report/WSSSPE1_summary_report.tex
small change in opening

% TODO: Why are we doing case studies?
Many important issues related to scientific software sustainability were
discussed in the previous sections. In this section we discuss some of the
software projects as case-studies to better understand the relevance of those
issues and how are they connected to the software sustainability and related
factors.

>>>>

% TODO: Why are we doing case studies?
In this section, we discuss some of the software projects as case-studies to
better understand the points discussed during the workshop and described in the
previous sections. We dive deeper to find how are they affected by the
sustainability issues in practice.
